MINOS Handover Plots

### 2023-08-01 minos/validation/handovers.Rmd
Now generating an inflated population for every year in raw data, and updated handovers to use this inflated population for validation

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

@@

@@

handover_boxplots(raw.dat, base.dat, 'hh_income')
handover_lineplots(raw.dat, base.dat, "hh_income")

# raw.income2 <- raw.dat %>% 
#               dplyr::select(pidp, time, hh_income) %>%
#               filter(pidp %in% raw.income.wave1)
# 
# base.income <-  base.income2 <- base.dat %>%
#                                 dplyr::select(pidp, time, hh_income) %>%
#                                 filter(pidp %in% raw.income.wave1)
# 
# handover_lineplots(raw.d)
# ## Try a version where final_US is limited to only those present from wave 1 
# # onwards because the sample refreshments are messing with the plot
# raw.income.wave1 <- raw.dat$pidp[raw.dat$time == 2009]
# 
# raw.income2 <- raw.dat %>% 
#   dplyr::select(pidp, time, hh_income) %>%
#   filter(pidp %in% raw.income.wave1) %>%
#   group_by(time) %>%
#   summarise(income = mean(hh_income, na.rm = TRUE)) %>%
#   mutate(source = 'final_US')
# 
# base.income2 <- base.dat %>%
#   dplyr::select(pidp, time, hh_income) %>%
#   filter(pidp %in% raw.income.wave1) %>%
#   group_by(time) %>%
#   summarise(income = mean(hh_income, na.rm = TRUE)) %>%
#   mutate(source = 'baseline_output')
# 
# income2 <- rbind(raw.income2, base.income2)
# 
# # Now plot
# ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
#   geom_line() +
#   geom_vline(xintercept=start.year, linetype='dotted') +
#   labs(title = 'Household Income') +
#   xlab('Year') +
#   ylab('Income')
# 
# if (shall.we.save) {
#   ggsave(filename = 'hh_income_wav1.png',
#        plot = last_plot(),
#        path = save.path)
# }
# 
# raw.income.check <- raw.dat %>% 
#   dplyr::select(pidp, time, hh_income) %>%
#   filter(pidp %in% raw.income.wave1)
# 
# base.income.check <- base.dat %>%
#   dplyr::select(pidp, time, hh_income) %>%
#   filter(pidp %in% raw.income.wave1)
# 
# rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
#    raw.income.check, base.income.check)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, housing_quality)
base.s <- base.dat %>%
  select(pidp, age, time, housing_quality)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'housing_quality',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, neighbourhood_safety)
base.s <- base.dat %>%
  select(pidp, age, time, neighbourhood_safety)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'neighbourhood_safety',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, loneliness)
base.s <- base.dat %>%
  select(pidp, age, time, loneliness)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'loneliness',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
raw.nut <- raw.dat %>%
  select(pidp, age, time, nutrition_quality)
base.nut <- base.dat %>%
  select(pidp, age, time, nutrition_quality)

nut.spag <- rbind(raw.nut, base.nut)

spaghetti_plot(nut.spag, 'nutrition_quality',
               save = shall.we.save,
               save.path = save.path)

density_ridges(nut.spag, "nutrition_quality", 
               save = T, 
               save.path = save.path)

rm(raw.nut, base.nut, nut.spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, phealth)
base.s <- base.dat %>%
  select(pidp, age, time, phealth)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'phealth',
             save = shall.we.save,
             save.path = save.path)

rm(raw.s, base.s, spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, education_state)
base.s <- base.dat %>%
  select(pidp, age, time, education_state)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'education_state',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

>>>>

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'inflated_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

@@

# SAMPLE

```{r}
raw.n <- raw.dat %>%
  group_by(time) %>%
  count() %>%
  mutate(source = 'final_US')

base.n <- base.dat %>%
  group_by(time) %>%
  count() %>%
  mutate(source = 'baseline_output')

combined <- rbind(raw.n, base.n)
#combined$time <- as.factor(combined$time)

ggplot(data = combined, aes(x = time, y = n, group = source, color = source, fill = source)) +
  geom_vline(xintercept=start.year, linetype='dotted') +
  geom_col(position='dodge') +
  labs(title = 'Sample size over time')
```

# Check Weights

```{r}
# raw.weight <- raw.dat %>%
#   group_by(time) %>%
#   summarise(sum.weight = sum(weight, na.rm = TRUE))
# 
# ggplot(data = raw.weight, aes(x = time, y = sum.weight)) +
#   geom_line()
```

@@

handover_boxplots(raw.dat, base.dat, 'hh_income')
handover_lineplots(raw.dat, base.dat, "hh_income")
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, housing_quality)
# base.s <- base.dat %>%
#   select(pidp, age, time, housing_quality)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'housing_quality',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, neighbourhood_safety)
# base.s <- base.dat %>%
#   select(pidp, age, time, neighbourhood_safety)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'neighbourhood_safety',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, loneliness)
# base.s <- base.dat %>%
#   select(pidp, age, time, loneliness)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'loneliness',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.nut <- raw.dat %>%
#   select(pidp, age, time, nutrition_quality)
# base.nut <- base.dat %>%
#   select(pidp, age, time, nutrition_quality)
# 
# nut.spag <- rbind(raw.nut, base.nut)
# 
# spaghetti_plot(nut.spag, 'nutrition_quality',
#                save = shall.we.save,
#                save.path = save.path)
# 
# 
# density_ridges(nut.spag, "nutrition_quality", 
#                save = T, 
#                save.path = save.path)
# 
# rm(raw.nut, base.nut, nut.spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, phealth)
# base.s <- base.dat %>%
#   select(pidp, age, time, phealth)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'phealth',
#              save = shall.we.save,
#              save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, education_state)
# base.s <- base.dat %>%
#   select(pidp, age, time, education_state)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'education_state',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

```{r}

```
